Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-19 index.Rmd
plots

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Histogram of the New Index",
               renderPlot({
                 feature = Index_Score_rect()
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable_index()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable_index()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react_index())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react_index())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

>>>>

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderPlot({
                 pnl_plot(High_feature_Hedged_react())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderPlot({
                 pnl_plot(Low_feature_Hedged_react())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Histogram of the New Index",
               renderPlot({
                 feature = Index_Score_rect()
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               renderTable({
                 feature_IRATStable_index()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               renderTable({
                 feature_CALtable_index()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               renderPlot({
                 pnl_plot(High_feature_Hedged_react_index())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               renderPlot({
                 pnl_plot(Low_feature_Hedged_react_index())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```
